Stemmer Tool Manual

### 2018-03-14 tex/merf/OldSubmission/tool.tex
old submission files

The \framework framework is illustrated in the flow diagram of
Figure~\ref{f:overview}.
The Arabic text and the reference tag chunks are the primary inputs to \framework. 
Solutions, morphology-based Boolean formulae, tags, 
morphology-based regular expressions, 
tag chunks, relation and action definitions, and data structures expressing entities 
and relations are input and output data to processes. 
The morphological analyzer (Sarf), $Syn^k$ detector, 
GUI for Boolean formulae definition, 
visualization annotator, GUI for regular expression and action definition, 
Boolean formula simulator, regular expression simulator, 
relation extraction and action execution, and difference and statistical analyzer 
are processes.

%The user interacts with \framework~through a user-friendly interfaces to 
%specify morphology-based Boolean formulae and regular expressions 
%and associate them with tag types that are in turn associated with
%visualization legends such as 
%foreground and background colors and fonts. 
%The user also associates code actions to parts of the regular expressions.
%The user can also declare relations between matches using the relation
%editor.

@@

The sets $E, A,$ and $L$ denote all English words, Arabic words, 
and Arabic lexicon words, respectively. 
We have $\GG \subset E$ and $\ss \subset L \subset A$. 
Function $\alpha: \ss \rightarrow 2^{\GG}$ maps Arabic stems to 
subsets of related English glosses. %; e.g. $g_{s} = \alpha(s)\subset 2^{\GG}$.
Function $\gamma: L \rightarrow 2^{\ss}$ maps Arabic lexicon words to subsets 
of relevant Arabic stems. %; e.g. $s_{l} = \gamma(l)\subset 2^{\ss}$.

Given a word $w\in L$, 
$Sy(w)=\{u\mid u\in \ss \land\exists s\in \gamma(w)\land~\alpha(u)\cap\alpha(s)\neq\emptyset\}$
is the set of Arabic stems 
directly related to $w$ through the gloss map.

Let $Sy^{i}(w)$ denote stems related to $w$ using the gloss map of order $i$ recursively such that
$Sy^{1}(w) = Sy(w)$ and
$Sy^{i+1}(w)=\{u\mid u\in S\land\exists s\in Sy^{i}(w)\land~\alpha(u)\cap\alpha(s)\neq\phi\}$.
Formally, $Syn^k(w) = \bigcup\limits_{i=1}^{k} Sy^{i}(w)$ for $i\in[1 \ldots k]$.

The example in Figure~\ref{fig:introsynEx} illustrates the computation. 
The word \RL{mA'}is related to \RL{n.d.h}through the gloss intersection \cci{water}. 
The $Syn^2$ feature relates 
the words \RL{mA'} and ``\RL{r^s^s}'' since \RL{n.d.h} and \RL{r^s^s} 
have the gloss intersection \cci{spray}.

\begin{figure}[tb!]
\setcode{utf8}
\begin{center}
  \resizebox{0.7\columnwidth}{!}{ 
  	{\relsize{-2} \input{figures/syn2ex.tex}} }
\setcode{standard}
\caption{$Syn^2($\RL{mA'}$)$}
\label{fig:introsynEx}
\end{center}
\end{figure}

\subsection{MRE: Morphology-based regular expressions}

Let ${\cal O} = \{ \mathit{isA}, \mathit{contains}\}$ be the set of atomic term 
predicates, and let ${\cal F} = \{ \pp, \ss, \xx, \PP, \GG, \AC\}$ be the 
set of morphological features. 
Given a word $w$, a morphological feature $A\in{\cal F}$, 
a user defined constant feature value $CF\in A$, and an integer 
$k, 1\le k\le 7$, 
the following are morphology-based atomic terms (MAT). 
\begin{itemize}
  \item $a(w):= \exists m \in M(w). m=\langle p,s,x,P,G,C\rangle. r \circ CF$
where $\circ \in {\cal O}$, $r \in \{p,s,x,P,G,C\}$, and $r\in A$.
Informally, a solution vector of $w$ exists with
a feature containing (or exactly matching) $CF$. 
\item $a(w) := w \in Syn^k(CF), CF \in \ss$.
  Informally, this checks $w$ is an extended synonym of a stem $CF$. 
\end{itemize}

A morphology-based Boolean formula (MBF) is of the following form. 
\begin{itemize}
  \item $a$ and $\neg a$ are MBF formulae where $a$ is a MAT and $\neg$ is the negation operator. 
  \item $(f \vee g)$ is an MBF where $f$ and $g$ are MBF formulae, 
    and $\vee$ is the disjunction (union) operator. 
\end{itemize}
Formula $N$ in Figure~\ref{fig:motiv} checks whether a solution has a category
feature matching category {\tt Name\_of\_Person}.
Formula $R$ is the disjunction of MAT terms that check for
solutions matching stems such as \RL{qrb} (near) and \RL{fy} (in).

A morphology-based regular expression (MRE) is one of the following. 
\begin{itemize}
\item $m$ is an MRE where $m$ is an MBF.
\item $fg$ is an MRE denoting a concatenation operation
  where $f$ and $g$ are both MRE expressions. This is 
  satisfied by a match of $f$ followed by a match of $g$. 
\item $f*,f+,f$\textasciicircum$x,$ and $f?$ are MRE expressions where $f$ is an MRE,
  and are satisfied by zero or more matches, one of more matches, up to $x$ matches, 
  and zero or only one match of $f$, respectively.
\item $f\& g,$ (conjunction) and $f|g$ (disjunction) are  MRE expressions where 
  $f$ and $g$ are MRE expressions, and are satisfied by a 
  a match of both $f$ and $g$, 
  and a match of either $f$ or $g$, respectively. 
\end{itemize}
We denote by $\ldbrack f\rdbrack$ the set of matches of an MRE $f$.

@@

@@

Once \framework computes all match trees, it traverses each match to 
execute the user defined \cci{pre-match} actions in pre-order manner
and the \cci{on-match} actions in post-order manner.

@@

The set of tag types ${\cal T}$ contains tuples of the form $\langle l,f,d\rangle$ 
where $l$ is a text label with a descriptive name, 
$f$ is an MRE, and $d$ is a visualization legend 
with font and color information.

For each word $t_i\in T, 0\le i < n, n=|T|$ 
\framework computes a Boolean value 
($\{\mathit{true}, \mathit{false}\}$)
for all MBFs. 
Then, it computes the set of MBF tags
$R_i=\{(t_i,tt)| tt=\langle l,f,d\rangle \wedge
f~\mathit{is~an~MBF} \wedge f(t_i)\} \subseteq T \times {\cal T}$
which tags a word $t_i$ with $\mathit{tt}$ 
iff the MBF $f$ associated with
tag type $\mathit{tt}$ is true for $t_i$.

@@

\framework simulates the generated NFA over the sequence of tag sets 
matching the MBF formulae.
A simulation match $m$ of an expression $f$ is a tree where the root is the 
MRE expression, the internal nodes are the MRE and MBF operations, and the 
leaves are matches of the MAT terms of $f$.
The leave matches form a vector of tags
$\langle r_k,r_{k+1},\dots,r_j\rangle$ 
corresponding to the text sequence 
$\langle t_k,t_{k+1},\dots,t_j\rangle$ where $r_{\ell}\in R_{\ell},0\le k\le \ell \le j < n$.
%
%If the simulation has a match $\langle r_m,r_{m+1},\dots,r_n\rangle$ 
%where $0\le m\le n$, 
%the next simulation starts at $R_{n+1}$. 
%This disallows overlap of matches for the same MRE. 
%
%In case the NFA simulation has no match, 
%the next simulation starts at $R_{m+1}$. 
If we have more than one match %starting at $R_k$ where $0\le k\le n$, 
\framework returns the longest. 
%
Figure~\ref{fig:motiv}(b) shows two match trees of $\mathit{dir}$ extracted 
from the text of Figure~\ref{fig:intromotiv}.
\RL{dby} and \RL{mwl} are leaf nodes referring to name of place tags ($P$). 
The $+$, $|$, and $?$ MRE operations
are internal nodes.

@@

\begin{figure}[tb!]
\centering
\resizebox{0.7\columnwidth}{!}{
	\relsize{-1} \input{figures/reNFA.tex}
}
  \caption{Equivalent NFA of direction expression}
  \label{fig:nfaEx}
\end{figure}
\transtrue
\setcode{standard}

@@

\framework computes the relational entities in a user defined 
relation $R=\ldbrack \langle e_1,e_2,r\rangle \rdbrack$
$\subseteq \ldbrack e_1 \rdbrack \times \ldbrack e_2 \rdbrack \times \ldbrack r \rdbrack$ 
to be the elements of $\ldbrack e_1 \rdbrack \times \ldbrack e_2 \rdbrack \times \ldbrack r \rdbrack$
with the smallest nonzero positive distance between the source and the destination
where the distance is the number of words between the matches.

@@

For the first match \RL{brj _hlyfT bAlqrb mn AltqA.t` Al-'-wl},
the matches of $e_1,~e_2,~o_2,$ and $r$ are 
\RL{brj _hlyfT}(Khalifa tower), \RL{AltqA.t` Al-'-wl}(intersection 1), 
\RL{mn}(from), and \RL{bAlqrb}(next to), respectively. 
\framework~doesn't construct the relation $\langle r, e_1, o_1\rangle$ 
since $o_1$ has no match. 
Therefore, we get the upper part of the entity-relation graph shown 
in Figure~\ref{fig:intromotiv}.

>>>>

This section assumes that the user passed a set of text documents and 
specified a set of tag types using the interactive user friendly
interface of \framework. 
Let $T=\langle t_1,t_2,\ldots,t_M\rangle$ be a set of Arabic words denoting the 
text documents, and let ${\cal T}$  be the 
set of tag types each with an associated formula. 
\framework uses Sarf~\cite{ZaMaColing2012DemosSarf},
to compute a set of morphological solutions $M(t)=\{m_1,m_2,\ldots,m_N\}$
for each word $t\in T$.

Recall from Section~\ref{sec:overview} 
that \pp, \ss, \xx, \PP, \GG, and \AC~denote the set of prefixes, stems, 
suffixes, POS, gloss, and category tags, respectively. 
Each morphological solution $m\in M(t)$ is a tuple of the form 
$\langle p,s,x,P,G,C\rangle\in \pp \times  \ss\times \xx\times \PP\times\GG \times \AC$.
%where $p\in \pp, s\in \ss, x\in \xx, P \in \PP, G \in \GG,$ and $C \in \AC$.

In what follows we formally present 
the extended synonymy feature, 
the morphology-based atomic terms (MAT), 
the morphology-based Boolean formulae (MBF), 
the morphology-based regular expressions (MRE), 
the computational actions, and the user defined relational entities.

%\begin{table}[tb!]
%\centering
%\caption{Example of computing $Sy(l_{5})$ and $Sy^{1}(l_{5})$}
%\begin{tabular}{|c|c|c|c|c|c|}
%\hline
%$s$ & $\alpha(s) $ & $\alpha(l_{1})\cap\alpha(s)$ & $\alpha(l_{2})\cap\alpha(s)$ & $\alpha(l_{3})\cap\alpha(s)$ \\
%\hline
%$l_{1}$ & $e_{1}$,$e_{2}$ & $e_{1}$,$e_{2}$ & $e_{2}$ & $e_{2}$ \\
%\hline
%$l_{2}$ & $e_{2}$ & $e_{2}$ & $e_{2}$ & $e_{2}$ \\
%\hline
%$l_{3}$ & $e_{2},e_{3}$ & $e_{2}$ & $e_{2}$ & $e_{2},e_{3}$ \\ 
%\hline
%$l_{4}$ & $e_{3},e_{4}$ & $\emptyset$ & $\emptyset$ & $e_{3}$ \\
%\hline 
%\end{tabular}
%\label{table:syex}
%\end{table}
%

\begin{figure}[tb!]
\setcode{utf8}
\begin{center}
  \resizebox{\columnwidth}{!}{ 
  	{\relsize{-3} \input{figures/syn2ex.tex}} }
\setcode{standard}
\vspace{-2em}
\caption{$Syn^2($\RL{mA'}$)$}
\vspace{-3em}
\label{fig:introsynEx}
\end{center}
\end{figure}

@@

The sets $E, A,$ and $L$ denote all English words, Arabic words, 
and Arabic lexicon words, respectively. 
We have $\GG \subset E$ and $\ss \subset L \subset A$. 
Function $\alpha: \ss \rightarrow 2^{\GG}$ maps Arabic stems to 
subsets of related English glosses; e.g. $g_{s} = \alpha(s)\subset 2^{\GG}$.
Function $\gamma: L \rightarrow 2^{\ss}$ maps Arabic lexicon words to subsets 
of relevant Arabic stems; e.g. $s_{l} = \gamma(l)\subset 2^{\ss}$.

Given a word $w\in L$, 
$Sy(w)=\{u\mid u\in \ss \land\exists s\in \gamma(w)\land~\alpha(u)\cap\alpha(s)\neq\emptyset\}$
is the set of Arabic stems 
directly related to $w$ through the gloss map.
For example, consider % the example of Table~\ref{table:syex} where
$\ss$ = $\{l_{1}, l_{2}, l_{3}, l_{4}\}$, 
$L$ = $\ss \cup \{l_{5}, l_{6}\}$,
$\GG$ = $\{e_{1}, e_{2}, e_{3}, e_{4}\}$, 
$E$ = $\GG \cup \{e_{5}, e_{6}\}$, 
$\alpha$ = $\{ \mathbf{(l_{1}, \{e_{1}, e_{2}\})}, 
\mathbf{(l_{2}, \{e_{2}\})}, (l_{3}, \{e_{2}, e_{3}\}),
(l_{4}, \{e_{3}, e_{4}\})\}$,  and 
$\gamma$ = $\{ (l_{1}, \{l_{1}\}),  
  (l_{2}, \{l_{2}\}),  (l_{3},  \{l_{3}\}), (l_{4},  \{l_{4}\}), \\
\mathbf{(l_{5}, \{l_{1}, l_{2}\})},  (l_{6}, \{l_{4}\})\}$.

Given the Arabic word $l_{5}$ with stems
$\gamma(l_5) = \{l_{1},l_{2}\}$ and related glosses
$\alpha(l_{1}) = \{e_{1},e_{2}\} \cup \alpha(l_{2}) = \{e_{2}\}$. 
%Table~\ref{table:syex} illustrates the process of computing 
%$Sy(l_5)$ is the stems whose glosses have
%some intersection with the glosses related to $l_{5}$. 
Stem $l_3$ is in $Sy(l_5)$ since $\alpha(l_{3})\cap\alpha(l_{1}) = \{e_{2}\}\not=\emptyset$;
similarly, for  $l_1$ and $l_2$. However, $l_4$ is not in $Sy(l_5)$ since 
$\alpha(l_{4})\cap\alpha(l_{5}) = \emptyset$.
Consequently, $Sy(w) = \{l_{1},l_{2},l_{3}\}$.

Let $Sy^{i}(w)$ denote stems related to $w$ using the gloss map of order $i$ recursively such that
$Sy^{1}(w) = Sy(w)$ and
$Sy^{i+1}(w)=\{u\mid u\in S\land\exists s\in Sy^{i}(w)\land~\alpha(u)\cap\alpha(s)\neq\phi\}$.
For example, $Sy^{2}(l_{5})$ includes  $l_{4}$ since $(\alpha(l_{3})\cap\alpha(l_{4}))\neq\emptyset$. 
Formally, $Syn^k(w) = \bigcup\limits_{i=1}^{k} Sy^{i}(w)$
to be the union of $Sy^{i}(w)$ for $i\in[1 \ldots k]$.

The example in Figure~\ref{fig:introsynEx} illustrates the computation. 
%Words \RL{mA'}, \RL{n.d.h}, and \RL{r^s^s} and their glosses
%\{water\}, \{water, leak, spray\}, and \{spray, splatter\}, respectively,
%shown in the example of Figure~\ref{fig:introsynEx}. 
The word \RL{mA'} is related to \RL{n.d.h} through the gloss intersection \cci{water}. 
The $Syn^2$ feature relates 
the words \RL{mA'} and ``\RL{r^s^s}'' since \RL{n.d.h} and \RL{r^s^s} 
have the gloss intersection \cci{spray}.

%\begin{figure}[tb!]
%\setcode{utf8}
%\begin{center}
%  \resizebox{0.8\columnwidth}{!}{ 
%  	{\relsize{-3} \input{figures/syn2ex.tex}}
%  }
%  \setcode{standard}
%  \caption{$Syn^2($\RL{.t`Am}$)$}
%  \label{fig:synEx}
%\end{center}
%\end{figure}

\vspace{-3em}
\subsection{MRE: Morphology-based regular expressions}

Let ${\cal O} = \{ \mathit{isA}, \mathit{contains}\}$ be the set of atomic term 
predicates, and ${\cal F} = \{ \pp, \ss, \xx, \PP, \GG, \AC\}$ be the 
set of morphological features. 
Given a word $w$, a morphological feature $A\in{\cal F}$, 
a user defined constant feature value $CF\in A$, and an integer 
$k, 1\le k\le 7$, 
the following are morphology-based atomic terms (MAT). 
\begin{itemize}
  \item $a(w):= \exists m \in M(w). m=\langle p,s,x,P,G,C\rangle. r \circ CF$
where $\circ \in {\cal O}$, $r \in \{p,s,x,P,G,C\}$, and $r\in A$.
Informally, a solution vector of $w$ exists with
a feature containing (or exactly matching) $CF$. 
\item $a(w) := w \in Syn^k(CF), CF \in \ss$.
%\item $a(w) := \exists s\in \gamma(w).s\in Syn^k(CF)
%  \textit{where} k\in\{1,\dots,7\}$. 
  Informally, this checks $w$ is an extended synonym of a stem $CF$. 
\end{itemize}

%Consider the motivational example introduced in Section~\ref{sec:motivation}. 
%Some of the MATs defined are:

%\begin{itemize}
%\item $t_1=C~isA~Name\_of\_Person$
%\item $t_2=s~isA~\RL{qrb}$
%\item $t_3=s~isA~\RL{fy}$
%\end{itemize}

%$t_1$ checks whether a word has the category {\tt Name\_of\_Person}.  
%$t_2$ checks whether the stem of a word is \RL{qrb} (near). 
%$t_3$ checks whether the stem of a word is \RL{fy} (in). 
%Note that a word can be tagged with more than one MAT.

A morphology-based Boolean formula (MBF) is of the following form. 
\begin{itemize}
  \item $a$ and $\neg a$ are MBF formulae where $a$ an MAT, where
    $\neg$ is the negation (complement) operator. 
  \item $(f \vee g)$ is an MBF where $f$ and $g$ are MBF formulae, 
    and $\vee$ is the disjunction (union) operator. 
\end{itemize}
Formula $N$ in Figure~\ref{fig:motiv} checks whether a solution has a category
feature matching category {\tt Name\_of\_Person}.
Formula $R$ is the disjunction of MAT terms that check for
solutions matching stems such as \RL{qrb} (near) and \RL{fy} (in).

A morphology-based regular expression (MRE) is one of the following. 
\begin{itemize}
\item $m$ is an MRE where $m$ is an MBF.
\item $fg$ is an MRE denoting a concatenation or a sequencing operation
  where $f$ and $g$ are both MRE expressions. This is 
  satisfied by a match of $f$ followed directly by a match of $g$. 
\item $f*,f+,f$\textasciicircum$x,$ and $f?$ are MRE expressions where $f$ is an MRE,
  and are satisfied by zero or more matches, one of more matches, up to $x$ matches, 
  and zero or only one match of $f$, respectively.
%  This refers to the {\em Kleene-star} operation, and is satisfied by 
%  zero or more matches of $f$.
%\item $f+$ is an MRE where $f$ is an MRE. 
%This operation is interpreted as one or more matches of $f$.
%\item $f$\textasciicircum$x$ is an MRE where $f$ is an MRE and $x \in \mathbb{N^*}$. 
%This is interpreted as zero or more matches of $f$ up to $x$ matches.
%\item $f?$ is an MRE where $f$ is an MRE. 
%This is interpreted as zero or one occurrence of MRE $f$.
\item $f\& g,$ (conjunction) and $f|g$ (disjunction) are  MRE expressions where 
  $f$ and $g$ are MRE expressions, and are satisfied by a 
  a match of both $f$ and $g$, 
  and a match of either $f$ or $g$, respectively. 
\end{itemize}
We denote by $\ldbrack f\rdbrack$ the set of matches of an MRE $f$.

@@

%\itodo{handle the following}
%Moreover, \framework~defines the 
%{\em default cross-reference} relation between two 
%entities $e_1$ and $e_2$ as
%$cr(e_1,e_2) := e_1.text \in Syn^2(e_2.text)$.
%\itodo{end of handle the following (:)}

@@

Once \framework computes all match trees, it traverses each match to 
execute the user defined \cci{pre-match} actions in a pre-order manner
and the \cci{on-match} actions in a post-order manner.
% as illustrated in the code of Figure~\ref{fig:actions-traverse}.

%In addition the user can also specify code headers to associate the expressions 
%with proprietary code such as declaring global variables and including user libraries.

%\begin{figure}[tb!]

%\begin{Verbatim}[fontsize=\relsize{-2},frame=lines,label=Match tree traverse to execute actions,commandchars=\\\[\]]
%traverse (node) {    //node is the match tree
%  pre-match(node)    //call user defined pre-match function
%  foreach child in node.children
%    traverse(child)  //recursively traverse children in tree
%  on-match(node)}    //call on-match function 
%\end{Verbatim}

%\begin{Verbatim}[fontsize=\relsize{-2},frame=lines,label=\cci{On-match} example,commandchars=\\\[\]]
%cout << \fvtextcolor[red][$s2.text];
%isHundred = true;
%if(current == 0)  {
%  currentH=\fvtextcolor[red][$s2.number];
%} else if(!isKey) {
%  currentH= current * \fvtextcolor[red][$s2.number];
%  current = 0;
%} else {
%  currentH = \fvtextcolor[red][$s2.number]; }
%isKey = false;
%\end{Verbatim}

%\caption{User-defined computational actions} 
%%(a) match tree traverse & (b) example \cci{on-match} action
%\label{fig:actionEx}
%\label{fig:actions-traverse}
%\end{figure}

%Consider the sample code action shown in Figure~\ref{fig:numnormalgo} (TMB algorithm). 
%This code action is used in the number normalization case study of Section~\ref{sec:results}. 
%The variables \cci{isHundred}, \cci{isKey}, \cci{current}, and \cci{currentH} are global variables declared by the user. 
%The use of \cci{cout} requires the user to include the \cci{iostream} library. 
%In the code the user can use the API with the \$ sign with an expression name to retrieve features of the match expressions. 
%In this example, the user prints the sub-expression text and processes its numerical value.
%
%The use can access the morphological features with the API {\tt \$sub\_expression\_name.matches}.
%The API returns a vector of morphological solutions where each solution contains the stem, 
%arrays of affixes (prefixes and suffixes), stem gloss, arrays for affix glosses, 
%stem POS, and arrays for affix POS tags.

@@

The set of tag types ${\cal T}$ contains tuples of the form $\langle l,f,d\rangle$ 
where $l$ is a text label with a descriptive name, 
$f$ is an MRE expression, and $d$ is a visualization legend
%The visualization legend describes how the tags should be displayed to the user 
that contains font and color information.
%such as the foreground and background colors, the
%font size, weight, and style.

For each word $t_i \in T, 0\le i < n, n=|T|$ 
\framework computes a Boolean value 
($\{\mathit{true}, \mathit{false}\}$)
for all MBF formulae. 
and computes the set of MBF tags
$R_i=\{(t_i,tt)| tt=\langle l,f,d\rangle \wedge
f~\mathit{is~an~MBF} \wedge f(t_i)\} \subseteq T \times {\cal T}$
which tags a word $t_i$ with $\mathit{tt}$ 
iff the MBF formula $f$ associated with
tag type $\mathit{tt}$ is true for $t_i$.

@@

\framework simulates the generated NFA over the sequence of tag sets 
matching the MBF formulae.
A simulation match $m$ of an expression $f$ is a tree where the root is the 
MRE expression, the internal nodes are the MRE and MBF operations, and the 
leaves are matches of the MAT terms of $f$.
The leave matches form a vector of tags
$\langle r_k,r_{k+1},\dots,r_j\rangle$ 
corresponding to the text sequence 
$\langle t_k,t_{k+1},\dots,t_j\rangle$ where 
where $r_{\ell}\in R_{\ell},0\le k\le \ell \le j < n$.
%
%If the simulation has a match $\langle r_m,r_{m+1},\dots,r_n\rangle$ 
%where $0\le m\le n$, 
%the next simulation starts at $R_{n+1}$. 
%This disallows overlap of matches for the same MRE. 
%
%In case the NFA simulation has no match, 
%the next simulation starts at $R_{m+1}$. 
If we have more than one match %starting at $R_k$ where $0\le k\le n$, 
\framework returns the longest. 
%
Figure~\ref{fig:motiv}(b) shows two match trees of $\mathit{dir}$ extracted 
from the text of Figure~\ref{fig:intromotiv}.
\RL{dby} and \RL{mwl} are leaf nodes referring to name of place tags ($P$). 
The $+$, $|$, and $?$ MRE operations
are internal nodes.

@@

\begin{figure}[tb!]
\centering
\resizebox{0.8\columnwidth}{!}{
	\relsize{-1} \input{figures/reNFA.tex}
}
  \caption{Equivalent NFA of direction expression}
\vspace{-2em}
  \label{fig:nfaEx}
\end{figure}
\transtrue
\setcode{standard}

@@

\framework computes the relational entities in a user defined 
relation $R=\ldbrack \langle e_1,e_2,r\rangle \rdbrack
\subseteq \ldbrack e_1 \rdbrack \times \ldbrack e_2 \rdbrack \times \ldbrack r \rdbrack$ 
to be the elements of $\ldbrack e_1 \rdbrack \times \ldbrack e_2 \rdbrack \times \ldbrack r \rdbrack$
with the smallest nonzero positive distance between the source and the destination
where the distance is the number of words between the matches.

@@

Similarly, for the  
first match \RL{brj _hlyfT bAlqrb mn AltqA.t` Al-'-wl},
the matches of $e_1,~e_2,~o_2,$ and $r$ are 
\RL{brj _hlyfT}(Khalifa tower), \RL{AltqA.t` Al-'-wl}(intersection 1), 
\RL{mn}(from), and \RL{bAlqrb}(next to), respectively. 
\framework~doesn't construct the relation $\langle r, e_1, o_1\rangle$ 
since $o_1$ has no match. 
Therefore, we get the upper part of the entity-relation graph shown 
in Figure~\ref{fig:intromotiv}.
